MS Keyrun Species, Environment, Data Formats

### 2020-07-09 docs/SpeciesEnvDat.Rmd
add blank spreadsheet

### Multispecies models

### Food web model

@@

@@

```{r getsurvey, eval=FALSE}

#survey link https://forms.gle/gfA3tKFKRBxf3Mu38
#results

@@

names(responses)[3] <- "StartYear"
names(responses)[5] <- "EndYear"
names(responses)[7] <- "SurvSeason"
names(responses)[9] <- "FishSeason"
names(responses)[11] <- "SpatialGB"

>>>>

The `ecodata` R package has up to date information at the Georges Bank EPU scale as listed here: https://noaa-edab.github.io/ecodata/landing_page.

Current time series in ecodata:
```{r ecodata}

#remotes::install_github("noaa-edab/ecodata",build_vignettes=TRUE)
library(ecodata)

ecodsets <- data(package = "ecodata")$result[, c("Item", "Title")]

datatable(ecodsets, rownames = FALSE, 
          options = list(pageLength = 25)
)

@@

How many models are implemented in R? See [discussion](https://docs.google.com/document/d/19FpJ8w2a-ZZ8ZY4ZmsnjlIilLeN1X9_Tz1dM-KsdOOw/edit#heading=h.kvnvc0pxyvqq) of pros and cons of using R data package for standardizing input datasets and making them available.

@@

```{r getsurvey}

#survey link https://forms.gle/gfA3tKFKRBxf3Mu38
#results link https://docs.google.com/spreadsheets/d/1sckY46jdyBa1Fhydw2syBawkjGPcHX4YwQmDCDBXcGU/edit#gid=284425233

@@

names(responses)[3] <- "Species"
names(responses)[5] <- "Environment"
names(responses)[7] <- "ModelInR"
names(responses)[8] <- "ModelUseR"
names(responses)[9] <- "RData"

We had `r nrow(responses)` responses.

### Species

Responses:
```{r}
# each row is a response with a comma delimited list of species
# string split each row to species
# tally by species
# histogram

#msspecies <- responses$Species

```{r} 
knitr::kable(responses$Rationale.for.species.included, col.names = "Species rationale", booktabs=TRUE)
```

### Environment

Responses:
```{r}
# each row is a response with a comma delimited list of environmental data
# string split each row to dataset name
# tally by dataset
# histogram

#msspecies <- responses$Environment

```{r} 
knitr::kable(responses$Rationale.for.environmental.time.series.included, col.names = "Environment rationale", booktabs=TRUE)
```

### Model programming frameworks

Responses:
```{r}
# these are multiple choice yes/no so just plot

#useR <- data.frame(ModelinR = responses$ModelinR,
